Object naming is context dependent - A case study on testing linguistic hypotheses on real-world image corpora

### 2018-07-12 papers/SiVL2018/resources.tex
Adds practical requirements for datasets

%(i) violates (R0: The data contains only examples of case11, and excludes examples of case22, case23, case33 (case33:) do humans choose a basic-level category (e.g.,~\refexp{dog}) even though the super-level (e.g.,~\refexp{animal}) would suffice to uniquely refer to the object?).

@@

The dataset also falls short in fully meeting requirement~R2 due to property~(iii)---it only covers 80~object categories---and constraint~(i) to some extent---we may not be able to reliably infer the basic-level from the data \cs{TODO: Example or remove last part}.

@@

\begin{table}[t]
	\begin{tabular}{lccc}
		\hline
		Resource & \multicolumn{3}{c}{No. categories $cat$ for which $*(cat, \text{ILSVRC})$:} \\
				& $\in$
				& superset
				& $\supset$\\
		\hline \hline
		\refcoco & 15 \\
		\refcocop & \\
		\flickr & \\
		\vgenome & \\
		\hline
	\end{tabular}
	\caption{Coverage of the categories by the $1,000$~synsets of the ILSVRC image classification challenge.  \label{tab:coverage_ilsvrc}}
\end{table}

>>>>

%(i) violates (R0: The data contains only examples of case11, and excludes examples of case22, case23, case33 (case33:) do humans choose the entry-level category (e.g.,~\refexp{dog}) even though the super-level (e.g.,~\refexp{animal}) would suffice to uniquely refer to the object?).

@@

The dataset also falls short in fully meeting requirement~R2 due to property~(iii)---it only covers 80~object categories---and constraint~(i) to some extent---we may not be able to reliably infer the entry-level from the data \cs{TODO: Example or remove last part}.

@@

\begin{table}[t]
	\begin{tabular}{lrrrr}
		\hline
			 			& \refcoco & \refcocop & \flickr & \vgenome \\
		\hline \hline
		total \#synsets	&	2580\\
		- match			&	112 \\
		- hyponyms		&	36 \\
		- hypernyms 	&	204 \\
		\hline
		%- not found		&	74 \\	
		%\hline
		\# 
				& \multicolumn{3}{c}{No. object names $obj$ for which $*(\text{synset}(obj), \text{ILSVRC})$:} \\
				& (obj)
				& in
				& hypernym
				& hyponym\\
		\hline \hline
		 	& 2580 & 112 & 204 & 36\\
		 	& 15 & 30 & 1 \cs{??}\\
		 	& \\
		\vgenome 	& \\
		\hline
	\end{tabular}
	\caption{Coverage of the object names in the datasets by WordNet and by the $1,000$~synsets of the ILSVRC image classification challenge. \#synsets(obj): number of object names for which synsets could be retrieved from WordNet;   \label{tab:coverage_ilsvrc}}
\end{table}

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
Adds practical requirements for datasets

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{booktabs}
\usepackage[usenames, dvipsnames]{color}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}

@@

\newcommand{\vgenome}{VisualGenome }
\newcommand{\referit}{ReferIt }
\newcommand{\refcoco}{RefCOCO }
\newcommand{\refcocop}{RefCOCO+ }
\newcommand{\flickr}{Flickr30k Entities }

@@

@@

\begin{itemize}
                 \item[R0] \textbf{Lexical choice}: \\
                 Which name did the speaker use to refer to the target object?
		\item[R1] \textbf{Lexical availability}: \\
		Which names are available for the target objects?  For instance, if we want to check whether a convertible is more often referred to with a basic-level category (\textit{car}) or a more specific one (\textit{convertible}) we need to know that a given object is a \textit{convertible}, and that \textit{convertible} is a sub-level concept of \textit{car} (and vehicle, etc.). Additionally, in \cite{graf2016animal}, the authors manually group object names used by speakers in terms of three levels (sub-level, basic-level, super-level). Thus, ideally, names would be grouped according to their taxonomic relations.
		\item[R2] \textbf{Contextual informativeness}: \\
		Which names are available for the other objects in the scene (i.e. distractors)?
		For instance, when the target is a convertible, we need to know that there are multiple convertible, cars, etc. to judge whether these concepts are ambiguous.

\end{itemize}

\section{Resources: What Do We Have?}
%\label{sec:resources}
%\textbf{TODO@Carina}\\
%\input{resources}

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{booktabs}
\usepackage[usenames, dvipsnames]{color}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
\usepackage{hyperref}

\usepackage{xspace}

@@

\newcommand{\vgenome}{VisualGenome\xspace}
\newcommand{\referit}{ReferIt\xspace}
\newcommand{\refcoco}{RefCOCO\xspace}
\newcommand{\refcocop}{RefCOCO+\xspace}
\newcommand{\flickr}{Flickr30k Entities\xspace}

@@

@Carina TODO:
\begin{itemize}
	\item requirements: \\ 
	add most specific name; (possible ways to obtain information: taxonomy, object detectors) \\
	add unconstraint object co-occurrences / unbiased as far as possible; \\
	rename R1? (lexical alternatives? candidate names?)
	\item title?
\end{itemize}

@@

\begin{itemize}
        \item[(1)] \textbf{Lexical choice}: \\
        Which name did the speaker use to refer to the target object?
		\item[(2)] \textbf{Lexical candidates}: \cs{"candidate" does not exclude the chosen name in contrast to "alternative"}\\
		%Which names are available for the target objects?  
		Which names are available for the target objects? 
		And how are they taxonomically related? 
		For instance, if we want to check whether a convertible is more often referred to with a basic-level category (e.g.,~\refexp{car}) or a more specific one (e.g.,~\refexp{convertible}) we need to know that a given object is a \cat{convertible}, and that \cat{convertible} is a sub-level concept of \cat{car} (and \cat{vehicle}, etc.). 
		%Additionally, in
		In \cite{graf2016animal}, the authors manually group object names used by speakers in terms of three levels (sub-level, basic-level, super-level). 
		Thus, ideally, %names 
		lexical candidates 
		would be grouped according to their taxonomic relations. 
		\item[(3)] \textbf{Contextual informativeness}: \\
		Which names are available for the other objects in the scene (i.e. distractors)?
		For instance, when the target is a \cat{convertible}, we need to know that there are multiple \cat{convertibles}, \cat{cars}, etc. to judge whether these concepts are ambiguous.
\end{itemize}

In practical terms, the prerequisite for Requirements~(2) and~(3) is, given an image, the information on \textbf{R1: the most specific category} of \textbf{each object} which is depicted in the image. 
A taxonomy, such as WordNet \cite{fellbaum1998wordnet}, could then be queried with these categories to retrieve their individual lexical candidates arranged by their taxonomic relations. \\
Furthermore, the information on the \textbf{R2: entry-level category} of an object could be used as a pivot to taxonomically group its lexical candidates.

With respect to linguistic data-driven experiments, the range of linguistic phenomena under study (see, e.g.,~Section~\ref{sec:object_naming} for phenomena in object naming) need to be observable in the data in order to study the interaction of their underlying factors. 
Hence, a further practical requirement is that the data, first, captures ideally all possible combinations of the factor values across all factors\footnote{For example, data that contains only images where target and distractor objects do not share any lexical candidates would not be appropriate}, and second, that it has been naturally produced in that speakers were not constraint in their choice of a name by external factors. 
We summarize this requirement by the term \textbf{R3: unconstraint}. 
Note that this requirement XXX \cs{@Sina ref to bias and paper you mentioned?}.
\section{Resources: What Do We Have?}
\label{sec:resources}
\input{resources}
